A Cross-Benchmark Comparison of 87 Learning to Rank Methods

### 2014-05-26 cikm_paper/paper.tex
volgorde klopt weer :)

EnergyNDCG & \cite{Freno2011} & \cite{Freno2011} & RankDE & \cite{Bollegala2011} & \cite{Sato2013} \\
FBPCRank & \cite{Lai2011} & \cite{Lai2011} & RankCSA & \cite{He2010} & \cite{He2010} \\

>>>>

EnergyNDCG & \cite{Freno2011} & \cite{Freno2011} & RankCSA & \cite{He2010} & \cite{He2010} \\
FBPCRank & \cite{Lai2011} & \cite{Lai2011} & RankDE & \cite{Bollegala2011} & \cite{Sato2013} \\
